### 2018-03-13 paper.Rmd
color over time

```{r load_packages, include = FALSE}
library("papaja")
```

@@

@@

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

>>>>

```{r load_packages, include = FALSE}
library("papaja")
library(tidyverse)
library(childesr)
library(directlabels)
```

@@

```{r}
colors <- c("black", "white", "red", "green", "yellow", "blue", "brown", 
             "orange", "pink", "purple")

graph_colors <- data_frame(color = colors,
                           graph_color = if_else(color == "white", 
                                                 "light gray", color))

color_counts <- get_types(role = c("Mother", "Father"), age = c(12,60), 
                              type = colors)

count_estimates <- color_counts %>%
  mutate(age = target_child_age / 30.5,
         age_bin = as.integer(floor(age / 6) * 6),
         color = tolower(gloss)) %>%
  group_by(age_bin, color, target_child_id) %>%
  summarise(count = sum(count)) %>%
  summarise(mean = mean(count, na.rm = T),
            sem = sd(count, na.rm = T) / sqrt(sum(!is.na(count)))) %>%
  left_join(graph_colors)

ggplot(count_estimates, aes(x = age_bin, y = mean, ymin = mean - sem, 
                            ymax = mean + sem, color = color, label = color)) + 
  geom_pointrange(position = position_dodge(.5)) + 
  geom_smooth(se = F) +
  facet_wrap(~ color) + 
  theme_classic(base_size = 14) +
  scale_color_manual(values = graph_colors$graph_color) +
  scale_x_continuous(breaks = seq(12, 60, 6)) + 
  geom_dl(method = list(dl.trans(x=x +.2), "last.qp", cex=1)) + 
  theme(legend.position = "none")
```

@@

# References
```{r create_r-references}
r_refs(file = "childesd.bib")
```
